---
title: "Defenders Analysis"
author: "Riu Sakaguchi"
date: "6/12/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```


```{r Libraries}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gdata)
library(stats)
library(stringr)
```


```{r Loading Data}
#Data
data <- readr::read_csv("https://www.stat2games.sites.grinnell.edu/data/defenders/getdata.php")

#Keeping Data after August 2nd
data <- data %>% mutate(Date = str_sub(Date, 1, 10))
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
data <- data %>% filter(Date >= as.Date("08/02/2019", format = "%m/%d/%Y"))

#Making Location and Virus a factor
data$Location <- as.factor(data$Location)
data$Virus <- as.factor(data$Virus)

#Arranging data
data <- data %>% arrange(GameNum)
```


```{r User Selection}
#Choose Level/Wave/Virus
level <- 4
wave <- 8

#For all data, include both red and blue
virus <- c("blue")
```



```{r Restricting Data}
#Filering level and wave
data <- data %>% filter(Level == level, Wave == wave)

#Removing Gamenum -1
data <- data %>% filter(!(GameNum == -1))


#Removing if there werent exactly 2 locations
Index <- numeric()

for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  temp$Location <- drop.levels(temp$Location)
  
  if(nlevels(temp$Location) != 2){
    Index <- append(Index, i)
  }
}
data <- data %>% filter(!(data$GameNum %in% Index))


#Filtering out players who used any upgrades
Index2 <- numeric()

for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  
  if("1Fast" %in% temp$Upgrade | 
     "1Far" %in% temp$Upgrade){
    
    Index2 <- append(Index2, i)
  }
}
data <- data %>% filter(!(data$GameNum %in% Index2))


#Filtering out players who have 5 or more rows
Index3 <- numeric()

for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  
  if(nrow(temp) >= 5){
    Index3 <- append(Index3, i)
  }
}
data <- data %>% filter(!(data$GameNum %in% Index3))


#Filtering out players if their two turrets only shot at one type of virus
Index4 <- numeric()

for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  temp$Virus <- drop.levels(temp$Virus)
  
  if(nlevels(temp$Virus) != 2){
    Index4 <- append(Index4, i)
  }
}
data <- data %>% filter(!(data$GameNum %in% Index4))

```


```{r Restructured Data (First half)}
#Making Restrucured Data frame

#Setting up
LocationCombination <- character()
MedicineCombination <- character()
Health <- numeric()
Funds <- numeric()

#Filling up vectors for the above 4 columns
for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  
  Funds <- append(Funds, temp$Funds[1])
  Health <- append(Health, temp$Health[1])
  
  #Location Combination
  loc <- sort(unique(temp$Location))
  LocationCombination <- append(LocationCombination, paste(loc[1], loc[2], sep = ""))
  
  #Medicine Combination
  temp1 <- temp %>% filter(Location == loc[1])
  temp2 <- temp %>% filter(Location == loc[2])
  
  med1st <- temp1$Medicine[1]
  med2nd <- temp2$Medicine[1]
  
  med1st <- str_sub(med1st, start = 5)
  med2nd <- str_sub(med2nd, start = 5)
  
  MedicineCombination <- append(MedicineCombination, paste(med1st, med2nd, sep = ""))
}

```


```{r Restructured Data (Second Half)}
#Fitering by player Virus choice
data <- data %>% filter(Virus %in% virus)

#Arrange data again
data <- data %>% arrange(GameNum)

#Setting Up
Destroyed <- numeric()
Shot <- numeric()

#Filling up vectors 
for(i in unique(data$GameNum)){
  
  temp <- data %>% filter(GameNum == i)
  
  Destroyed <- append(Destroyed, sum(temp$Destroyed))
  Shot <- append(Shot, sum(temp$Shot))
}


#Restrucured Data 
data_restructured <- data.frame(GameNum = sort(unique(data$GameNum)),
                                LocationCombination = LocationCombination,
                                MedicineCombination = MedicineCombination,
                                Health = Health, Funds = Funds,
                                Shot = Shot, Destroyed = Destroyed)

#Adding Missed and Percent Destroyed Column
data_restructured <- data_restructured %>% mutate(Missed = Shot - Destroyed,
                                                  PercentDestroyed = (Destroyed/Shot)*100)

```



```{r Interaction Plots}

#Destroyed
plot_destroyed <- interaction.plot(data_restructured$LocationCombination, data_restructured$MedicineCombination, data_restructured$Destroyed,
                 main = "Interaction Plot",
                 xlab = "Location Combination",
                 ylab = "Destroyed",
                 trace.label = "Med Combo",
                 col = c("blue1", "purple1", "violetred", "red1"),
                 lwd = 1.5) 


#Shot
plot_shot <- interaction.plot(data_restructured$LocationCombination, data_restructured$MedicineCombination, data_restructured$Shot,
                 main = "Interaction Plot",
                 xlab = "Location Combination",
                 ylab = "Shot",
                 trace.label = "Med Combo",
                 col = c("blue1", "purple1", "violetred", "red1"),
                 lwd = 1.5) 


#Percent Destroyed
plot_percentdestroyed <- interaction.plot(data_restructured$LocationCombination, data_restructured$MedicineCombination, data_restructured$PercentDestroyed,
                 main = "Interaction Plot",
                 xlab = "Location Combination",
                 ylab = "Percent Destroyed",
                 trace.label = "Med Combo",
                 col = c("blue1", "purple1", "violetred", "red1"),
                 lwd = 1.5) 
```



**Destroyed**
BR (12, 13, 14)
RR (24, 34) Turrets are too close to each other and since they are effective, many of the shots are not getting in and hence destroyed goes down as well.

**Shot**
RR (24, 34) As explained above, turrets are too close to each other and since they are effective, the turret that shoots second won't get their shot in. 

**Percent Destroyed**
RB and BR cross between 12 and 13.
BB and RR cross at 34 (Sample size could be an issue).

\
 

```{r Main Effects Plots (Location)}

#Location - Destroyed
main_ld <- data_restructured %>% group_by(LocationCombination) %>% summarize(Mean = mean(Destroyed))

ggplot(data = main_ld, aes(x = LocationCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Location Combination",
       x = "Location Combination", y = "Destroyed") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))





#Location - Shot
main_ls <- data_restructured %>% group_by(LocationCombination) %>% summarize(Mean = mean(Shot))

ggplot(data = main_ls, aes(x = LocationCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Location Combination",
       x = "Location Combination", y = "Shot") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))


#Location - Percent Destroyed
main_lpd <- data_restructured %>% group_by(LocationCombination) %>% summarize(Mean = mean(PercentDestroyed))

ggplot(data = main_lpd, aes(x = LocationCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Location Combination",
       x = "Location Combination", y = "Percent Destroyed") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))


```

**Destroyed**
Higher destroyed when turrets are closer to the entrance makes sense because we also get more shots in. 23 seems to be the worst location combination.

**Shots**
Again, we get more shots in when the turrets are placed closer to the entrance, and less as they are placed closer to the exit. 

**Percent Destroyed**
We see a U shape pattern with higher percentages at locations closest to the entrace and closest to the exit. Could most likley be due to the ratios of medicine combination at each location.

\


```{r Main Effects Plots (Medicine)}

#Medicine - Destroyed
main_md <- data_restructured %>% group_by(MedicineCombination) %>% summarize(Mean = mean(Destroyed))

ggplot(data = main_md, aes(x = MedicineCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Medicine Combination",
       x = "Medicine Combination", y = "Destroyed") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))


#Medicine - Shot
main_ms <- data_restructured %>% group_by(MedicineCombination) %>% summarize(Mean = mean(Shot))

ggplot(data = main_ms, aes(x = MedicineCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Medicine Combination",
       x = "Medicine Combination", y = "Shot") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))


#Medicine - Percent Destroyed
main_mpd <- data_restructured %>% group_by(MedicineCombination) %>% summarize(Mean = mean(PercentDestroyed))

ggplot(data = main_mpd, aes(x = MedicineCombination, y = Mean, group = 1)) +
  geom_point() +
  geom_path() +
  labs(title = "Main Effects Plot: Medicine Combination",
       x = "Medicine Combination", y = "Percent Destroyed") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  plot.title = element_text(hjust = 0.5, face = "bold"))

```


**Destroyed**
BB being the worst makes sense because there are more red viruses. The rest seem to be similar in terms of the number of viruses destroyed.

**Shot**
Perhaps RR is lower because it is supposed to be the most effective combination, and the second turrent might not be getting in shots. BB being the lowest might be a result of disproportionate location combinations

**Percent Destroyed**
This plot makes sense, BB being the lowest, RB and BR being around the same, and RR being the highest. 







```{r}
#Destroyed
anova_testDB <- aov(Destroyed ~ (LocationCombination  + MedicineCombination)^2, 
                  data = data_restructured)
summary(anova_testDB)


#Shot
anova_testSB <- aov(Shot ~ (LocationCombination  + MedicineCombination)^2, 
                  data = data_restructured)
summary(anova_testSB)


#Percent Destroyed
anova_testPB <- aov(PercentDestroyed ~ (LocationCombination  + MedicineCombination)^2, 
                  data = data_restructured)
summary(anova_testPB)
```


```{r Table}
table(data_restructured$LocationCombination,data_restructured$MedicineCombination)
```


```{r T-Tests}

#Two Group Data
data1213 <- data_restructured %>% filter(LocationCombination %in% c("12", "13"))
data1314 <- data_restructured %>% filter(LocationCombination %in% c("13", "14"))
data2434 <- data_restructured %>% filter(LocationCombination %in% c("24", "34"))


#Destroyed
t.test(data1213$Destroyed ~ data1213$LocationCombination)
t.test(data1314$Destroyed ~ data1314$LocationCombination)

#Shot
t.test(data1213$Shot ~ data1213$LocationCombination)
t.test(data1314$Shot ~ data1314$LocationCombination)

#Percent Destroyed
t.test(data1213$PercentDestroyed ~ data1213$LocationCombination)
t.test(data1314$PercentDestroyed ~ data1314$LocationCombination)
t.test(data2434$PercentDestroyed ~ data2434$LocationCombination)



```












